Online Updating of Variational Bayes for Forecasts of Vehicle Trajectory with Heterogeneous Driver Behaviour

### 2018-02-12 Cars/paper.tex
updates

\item These time series models (In this case a bivariate AR2) fit a parameter vector to capture the driver behaviour, which can depend both on the be very different from driver to driver (Chen 2017) which may depend on a particular vehicle's position relative to surrounding traffic.

@@

\item The self driving car is constantly observing additional information about the vehicles around it. Forecasts where the parameter vector is conditioned on this additional data should outperform forecasts conditioned on less data.
\item A three step strategy is employed to forecast the future trajectory of newly observed vehicles:

@@

\item This paper introduces a Variational Bayes updating method for the third step, where the posterior distribution of the new vehicles parameter vector is approximated, then this approximation is updated.

@@

\item Compare Bayes MAP point estimates to a neural network and constant acceleration / angle model.

@@

\section{Conclusion}
\begin{itemize}
\item Dynamic AR 2 models forecasting future acceleration and angles drastically improves forecasts of the future trajectory compared to the naive models.
\item Treating vehicles as heterogenous allows behaviour specific to an individual driver to be learned, further improving forecasts.
\item This requires constant models fits and updates, which can be made computationally feasible by updating previous Variational Bayes model fits, which incurs only a small performance hit relative to the more expensive standard VB and MCMC methods.
\end{itemize}

>>>>

\item A homogenous time series model shows a strong ability to predict the MAP trajectory
\itme An important part of this modelling is to capture the uncertainty of car trajectories, as the self-driving car must react to the possibility of collision even when that possibility is relatively small.
\item There are many sources of heterogeneity in drivers, from their individual driving styles to the conditions of traffic directly around them.
\item Including heterogeneity in the model will allow more dangerous vehicles to be identified, for example, 'lead-footed' drivers can have a larger variance on their acceleration.

@@

\item The self driving car must be able to estimate the parameter vector of newly observed cars, and update this parameter vector as it observes additional data.
\item Forecasts where the parameter vector is conditioned on this additional data should outperform forecasts conditioned on less data.
\item A three step strategy is employed to provide density forecasts for the future trajectory of newly observed vehicles:

@@

\item This paper uses standard Variational Bayes for the second step, and introduces an updating method for the third step; the posterior distribution of the new vehicles parameter vector is approximated, then this approximation is updated.

@@

\item Compare Bayes MAP point estimates to a neural network and naive models

@@

\section{Conclusion}
\begin{itemize}
\item Dynamic AR 2 models forecasting future acceleration and angles drastically improves forecasts of the future trajectory compared to the competing models.
\item Treating vehicles as heterogenous allows behaviour specific to an individual driver to be learned, improving logscores and forecast uncertainty.
\item This requires constant models fits and updates, which can be made computationally feasible by updating previous Variational Bayes model fits, which incurs only a small performance hit relative to the more expensive standard VB and MCMC methods.
\end{itemize}
